rotation_runs2019

### 2020-01-20 inst/documents/paper_figs_rotations201911.Rmd
working on paper figures

  # where the rotation runs saved
  #infolder <- "C:\\Dropbox\\resistanceResults\\rotations\\"
  infolder <- "C:\\Dropbox\\2017_Rotations for IRM\\SJ_Runs_Nov\\"

@@

# df_res_all$best_strategy <- ifelse(df_res_all$rot_minus_seq <= -(widthbin/2),"sequence", ifelse(df_res_all$rot_minus_seq > (widthbin/2), "rotation", "no_difference"))
# 
# ggplot(df_res_all, aes(x=rot_minus_seq, fill=best_strategy)) + 
#      geom_histogram(binwidth=widthbin, colour='white') + 
#      theme_minimal() +
#      theme(panel.grid.minor.y=element_blank())

# calc percentage difference between rotation and sequence
df_res_16$rms_percent <- 100 * df_res_16$rot_minus_seq / df_res_16$gens_seq

# best strategy calculation
# no_difference set to +/- half of widthbin set above
df_res_16$best_strategy <- ifelse(df_res_16$rot_minus_seq <= -(widthbin/2),"sequence", ifelse(df_res_16$rot_minus_seq > (widthbin/2), "rotation", "no_difference"))

@@

#rot_minus_seq, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("advantage of rotations over sequence in generations") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#rms (rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rms_percent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     scale_x_continuous(limits=c(-80,80), breaks = c(-60,-40,-20,0,20,40,60)) +
     xlab("percentage advantage of rotations over sequence in generations") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

    nruns_rot_20pc_better <- df_res_16 %>% 
                  filter(rot_minus_seq/gens_seq >= 0.2 ) %>%
                  summarise(n=n()) %>% 
                  unlist()

@@

# go through selected inputs and plot them on x with rot_minus_seq on y 
# TODO check whether this covers all the inputs we want to look at
in_cols <- c('cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs')

y <- 'rot_minus_seq'

@@

    x <- df_res_A[,in_cols]
    y <- df_res_A['rot_minus_seq']

@@

y <- 'rot_minus_seq'

ggplot(df_res_16, aes(x=dom_sel, y=dom_cos)) + 
     geom_point(shape=3, size=1, alpha=0.2, show.legend=FALSE) +
     theme_minimal() +
     geom_point(data=filter(df_res_16, rot_minus_seq/gens_seq >= 0.3 ), shape=1, size=1, col='red', alpha=0.8)

@@

>>>>

  # where the rotation runs saved
  #infolder <- "C:\\Dropbox\\resistanceResults\\rotations\\"
  #infolder <- "C:\\Dropbox\\2017_Rotations for IRM\\SJ_Runs_Nov\\"
  infolder <- "C:\\Dropbox\\2017_Rotations for IRM\\Results_Jan\\"

@@

# df_res_all$best_strategy <- ifelse(df_res_all$gens_rot_minus_seq <= -(widthbin/2),"sequence", ifelse(df_res_all$gens_rot_minus_seq > (widthbin/2), "rotation", "no_difference"))
# 
# ggplot(df_res_all, aes(x=gens_rot_minus_seq, fill=best_strategy)) + 
#      geom_histogram(binwidth=widthbin, colour='white') + 
#      theme_minimal() +
#      theme(panel.grid.minor.y=element_blank())

# calc percentage difference between rotation and sequence
df_res_16$rms_percent <- 100 * df_res_16$gens_rot_minus_seq / df_res_16$gens_seq

# best strategy calculation
# no_difference set to +/- half of widthbin set above
df_res_16$best_strategy <- ifelse(df_res_16$gens_rot_minus_seq <= -(widthbin/2),"sequence", ifelse(df_res_16$gens_rot_minus_seq > (widthbin/2), "rotation", "no_difference"))

@@

#gens_rot_minus_seq, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=gens_rot_minus_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("advantage of rotations over sequence in generations") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#rms (gens_rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rms_percent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     scale_x_continuous(limits=c(-80,80), breaks = c(-60,-40,-20,0,20,40,60)) +
     xlab("percentage advantage of rotations over sequence in generations") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

    nruns_rot_20pc_better <- df_res_16 %>% 
                  filter(gens_rot_minus_seq/gens_seq >= 0.2 ) %>%
                  summarise(n=n()) %>% 
                  unlist()

@@

# go through selected inputs and plot them on x with gens_rot_minus_seq on y 
# TODO check whether this covers all the inputs we want to look at
in_cols <- c('cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs')

y <- 'gens_rot_minus_seq'

@@

    x <- df_res_A[,in_cols]
    y <- df_res_A['gens_rot_minus_seq']

@@

y <- 'gens_rot_minus_seq'

ggplot(df_res_16, aes(x=dom_sel, y=dom_cos)) + 
     geom_point(shape=3, size=1, alpha=0.2, show.legend=FALSE) +
     theme_minimal() +
     geom_point(data=filter(df_res_16, gens_rot_minus_seq/gens_seq >= 0.3 ), shape=1, size=1, col='red', alpha=0.8)

@@

# new - mean mortality over whole sim
# slightly surprising that not much variation
# this one colours by best strategy in generation terms
# B1 suggests that runs where rotation is better may have
# lower mortality under rotation
# try to find a different way of showing that 
# (e.g. just plot gens_diff against mortality diff)

```{r figxmort-rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# ** mean mortality for rotations

# have a go at classifying gens_rot so I can use it to colour the mean mort bars
# cut(gens_rot, 5) this does that

ggplot(df_res_16, aes(x=mort_rot, fill = cut(gens_rot, 5))) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     geom_histogram(colour='darkgrey') + 
     #geom_histogram(binwidth=0.02, colour='darkgrey') + 
     #be interesting to color by generations to see if strategies that last longer have lower mortality ?
     #scale_fill_manual(values=colrs) +
     #scale_fill_continuous(aes(gens_rot)) +
     scale_fill_brewer(palette = 'greens') +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("mean mortality over all generations for rotation") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

```{r figxgens_rot_v_mort_rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# ** mean mortality for rotations

ggplot(df_res_16, aes(x=gens_rot, fill = cut(mort_rot, 5))) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     geom_histogram(colour='darkgrey') + 
     #geom_histogram(binwidth=0.02, colour='darkgrey') + 
     #be interesting to color by generations to see if strategies that last longer have lower mortality ?
     #scale_fill_manual(values=colrs) +
     #scale_fill_continuous(aes(gens_rot)) +
     scale_fill_brewer(palette = 'greens') +
     theme_minimal() +
     #xlim(-100,100) +
     #xlab("mean mortality over all generations for rotation") +
     #ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

```{r figxmort_rot_v_start_freqs, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# i expect that mean mort may be largely influenced by startfreqs, but remember when diff. there are multiple

# ** mean mortality for rotations

ggplot(df_res_16, aes(x=start_freqs, y=mort_rot)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     #geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     geom_hline(yintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_vline(xintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_point(shape='.') +
     geom_smooth() +
     #geom_abline() +
     # scale_fill_manual(values=colrs) +
     theme_minimal() +
     # #xlim(-100,100) +
     # xlab("advantage of rotations over sequence in mean mortality") +
     # ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

```{r figxmort-which-best-meanmort, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# ** using best strategy from generations calc above
# ** so trying to see if being better in generations terms
# ** has consequences for mean mortality

# **hmmm doesn't seem to work, all x differences 0
# because widthbin set to 10 above

#gens_rot_minus_seq, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=mort_rot_minus_seq, fill=best_strategy)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     #geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     geom_histogram(binwidth=0.02, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("advantage of rotations over sequence in mean mortality") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

#try to establish whether
#runs that have higher generations for rotations
#also have lower mean mortality

```{r figxmort-v-gens, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#gens_rot_minus_seq, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=gens_rot_minus_seq, y=mort_rot_minus_seq)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     #geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     geom_hline(yintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_vline(xintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_point(shape='.') +
     geom_smooth(method='lm') +
     #geom_abline() +
     # scale_fill_manual(values=colrs) +
     theme_minimal() +
     # #xlim(-100,100) +
     # xlab("advantage of rotations over sequence in mean mortality") +
     # ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

### 2020-01-20 inst/documents/rotation_runs2019.Rmd
working on paper figures

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
id_expt <- 'D4'

>>>>

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B1'
id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

### 2020-01-20 inst/documents/rotations_notes.Rmd
edit runs files
working on paper figures

@@

#check : gens_u_rot_minus_seq

currently 0 for all 200 runs of b2

Try some rotation_runs2019.Rmd with new outputs.
Get Sam to run new ones.

@@

~ consider renaming package to avoid conflict with CRAN rotations package insectrot rotinsect

@@

~ maybe just do annual rotation interval i.e. 10 ?

GET FREQUENCY RUNS sorted first (easier)
I could put the expt files all into one csv to start creating them, and divide into separate files later.

~ there is other stuff I still need in sensi_an_rotations1.Rmd - e.g. post-processing of outputs
~ could I have multiple experiments as columns in the same input file ?

~ add the random seed to the experiment file (and decide where it will be set)

~ investigate getting runs to name the output file with the date 
~ and create a similarly named metadata file that records run input params

@@

~ fix plot error when coverage==1

@@

~ maybe come back to i_in_use ribbons not meeting issue
~ add in some unit-tests ?
~ check how gens_under_thresh are counted in sensi_an_rotations1
    summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                     #finds insecticide in use = this one
                                     resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
                                 summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
                                 unlist()

~ how to deal with 'overshooting' leading to more generations under 50 when rotation intervals are shorter ? 
dfseq <- run_rot(rot_interval=0, max_gen = 300, migration=0.01, expo_hi=0.8, eff=0.8, cost=0.1, coverage=1)
dfrot <- run_rot(rot_interval=6, max_gen = 300, migration=0.01, expo_hi=0.8, eff=0.8, cost=0.1, coverage=1)
rot_plot_resistance(dfrot, df_resanother=dfseq, plot_refuge=FALSE)

@@

gens_dep_under50 is ugly and I need to rewrite in sensi_an_rotations !

@@

~ sort outputs which need to be time to resistance for planned rotations and RwR rotate when resistant. Sequence.

~ time under resitance threshold, e.g. 50%

>>>>

saved run file for sam to rotations_runs2020_sam.rmd

# 2020-01-10

sam did new runs

in paper_figs_rotations201911.rmd
~ replace rot_minus_seq with gens_rot_minus_seq

# 2020-01-13
looking at mean mortality from new runs

# 2020-01-17

A2 runs
run 94 (p95) rotation better
p109 sequence better

looking for the B1 runs where rotations are a bit better than sequences

@@

** convert single run plots to output total generations rather than gens-under-thresh **

Try some rotation_runs2019.Rmd with new outputs.

@@

~ consider renaming package to avoid conflict with CRAN rotations package insectrot rotinsect rotseq rotateinsect

@@

@@

@@

~ maybe come back to i_in_use ribbons not meeting issue
~ add in some unit-tests ?

@@

@@
